### 2015-06-23 paper/main.tex
update

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle Bayesian approaches, including EB, can naturally unify testing and estimation into a single framework -- testing is
simply estimation but with a point mass of some weight on the null hypothesis that an effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice, large-scale studies that assess many effects almost invariably focus on testing significance, and
controlling the FDR, rather than on estimating the sizes of the effect. 
The two new ideas highlighted above facilitate estimation as well as testing, and by providing easy-to-use software implementing our methods
we hope to promote and accelerate the shift in this direction.

@@

The $q$ value for observation $j$ is defined \cite{storey.03} as, roughly, the FDR for the set of observations that are at least as significant as observation $j$.
In a Bayesian analysis it is natural to order the significance of the hypotheses by $\fdr_j$, so we define
\begin{equation}
q_j := \FDR(\{k:\fdr_k \leq \fdr_j\}).
\end{equation}
In simple settings (e.g. symmetric effects, with the same standard error) $\fdr_j$ is a monotonic function of the $p$ value $p_j$, and so
\begin{equation}
q_j = \FDR(\{k:p_k \leq p_j\})
\end{equation}
which is close to the definition in \cite{storey.03}.

@@

 Here we introduce an EB method, which, for reasons discussed above, we call ``adaptive shrinkage" or ``ash".
 The method provides not only estimated $\fdr_j$ and q values, but also shrinkage point estimates and credible intervals for $\beta_j$,
 and estimates of the local false sign rate, defined below.

We begin by presenting the simplest version of our model, before embellishing it.
Instead of attempting to partition the (observed) $z$ scores or $p$ values into null and alternative components,
we use a model that partitions the (unobserved) effects $\beta_j$  into null and alternative components:
\begin{equation} \label{eqn:betaj}
\beta_j \sim \pi_0 \delta_0 + (1-\pi_0) g_1(\cdot)
\end{equation}
where $\delta_0$ denotes a point mass at 0, and $g_1$ denotes the (unknown) distribution of the non-zero $\beta_j$.
Thus $\pi_0$ denotes the proportion of effects that are null.

@@

Since the $\beta_j$ are unobserved, we need a model to connect the $\beta_j$ to observations. Here we
treat the estimates $\bhat_j$ as the observed data, and assume that they are noisy measurements of the true $\beta_j$ with given standard error
$\shat_j$:
\begin{equation} \label{eqn:bhat}
\bhat_j | \beta_j, \shat_j \sim N(\beta_j, \shat^2_j).
\end{equation}
This approach, which follows \cite{wakefield:2009}, 
should be a good approximation if $\bhat_j$ and $\shat_j$ are based on sufficiently many observations. We discuss below an improvement 
for moderate numbers of observations, based on replacing this normal likelihood with a $t$ likelihood.

Combining (\ref{eqn:betaj})-(\ref{eqn:bhat}), and assuming independence of the observations and effects for different $j$ (given $\pi_0,w_1,\dots,w_k$), yields
a hierarchical model for $\beta,\bhat$ given $\shat$, with unknown hyper-parameters $(\pi_0,w_1,\dots,w_k)$. To simplify notation we define $\pi_k := (1-\pi_0)w_k$ 
so that the unknown hyper-parameters can be written as a vector $\pi:=(\pi_0,\pi_1,\dots,\pi_K)$ whose elements are non-negative and sum to 1.
The usual empirical Bayes approach to fitting this model would involve two steps:
\begin{enumerate}
\item Estimate the hyperparameters $\pi$ by maximum likelihood, yielding a maximum likelihood estimate $\hat{\pi}$.
\item Compute quantities of interest (e.g. local fdr values, $q$ values, credible intervals etc.) from the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$.
\end{enumerate}
We make one modification to this procedure: instead of obtaining $\hat\pi$ by maximizing the likelihood, we instead maximise a penalized
likelihood, where the penalty (detailed below) encourages $\hat\pi_0$ to be as big as possible (within the constrains of the model and observed data). We use
this penalty here because in FDR appllications it is considered desirable to avoid underestimating $\pi_0$ so as to avoid underestimating the FDR. 
Both steps 1 and 2 are very straightforward: $\hat{\pi}$ can be obtained using a simple EM algorithm \cite{EM} to maximize the penalized likelihood, and the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$ are analytically available, each a mixture of a point mass on zero and $K$ normal distributions.
(Note that the simplicity of the EM algorithm in step 1 is due to our using a fixed grid for $\sigma_k$ in (\ref{eqn:g1}), instead of estimating $\sigma_k$,
which may seem more natural but is not straightforward when $\shat_j$ varies among $j$. This simple device may be useful in other applications.)

@@

\subsubsection*{More flexible prior component distributions}

@@

\subsubsection*{}

The conditional distributions $p(\beta_j | \bhat, \shat, \hat{\pi})$ encapsulate uncertainty in the values for $\beta_j$, combining information across
$j=1,\dots,J$. The combining of the information occurs through estimation of
$\pi$, which involves all of the data.
END OF DISCUSSION

--- NOte 
In principle we might prefer a full Bayes approach that accounts for uncertainty in $g$; however,
we believe that in most practical applications uncertainty in $g$ will not be the most important concern, and 
compromise this principle for the simplicity of the EB approach.

\begin{equation} \label{eqn:Lpi}
\bhat_j | \shat_j, \pi \sim \pi_0 N(\cdot; 0, \shat^2_j) + \sum_k \pi_k N(\cdot; 0,\sigma_k^2 + \shat^2_j) \quad \text{independently for $j=1,\dots,J$}.
\end{equation}

Our EB approach can now be simply stated. 
\begin{enumerate}
\item Estimate the parameters $\pi$ (and hence also the distribution $g_1$) by maximising the likelihood 
\begin{equation}
L(\pi) := \prod_j p(\bhat_j | \shat_j, \pi),
\end{equation}
where the terms of the likelihood are mixtures of the form (\ref{eqn:Lpi}). 
\end{enumerate}

 In outline, our goal is to perform Bayesian inference for the true effects $\beta$ using information in the summary statistics $\bhat,\shat$.
 That is we aim to compute the joint posterior distribution $p(\beta | \bhat,\shat)$.
This is connected with work by \cite{wakefield:2009} (see also \cite{johnson:2008}) who performs Bayesian inference
from summary statistics, computing $p(\beta_j | \bhat_j, \shat_j)$ for a single $j$,
with a specific fixed prior on $\beta_j$. Essentially we extend this to multiple $j$, using a hierarchical model to connect the observations.
 By working with summary statistics $\bhat, \shat$, rather than more refined data, we aim to produce generic methods that 
 can be applied whenever such summary data are available - just as \qvalue can be applied to any set of $p$ values for example.
Any attempt to produce generic methods is likely to involve a compromise between functionality and generality; 
we believe that by working with two numbers ($\bhat_j,\shat_j$) for each observation, rather than one ($p_j$ or $z_j$), 
we can gain substantially in functionality (e.g.~ we can estimate effect sizes, as well as testing, and we can take better account of variations in
measurement precision across units $j$) while losing only a little in generality.

We assume that (given $\shat$) the
effects $\beta_j$ are independent draws from some common ``prior" distribution $g$:
 \begin{equation} \label{eqn:beta}
 \beta_j \, | \, g, \shat \sim g(\cdot) \quad \text{independently for $j=1,\dots,J$.}
 \end{equation}
 A key assumption, which distinguishes our approach from previous work, is that $g$ is unimodal (and, optionally, symmetric). 
 We assume here that the mode is at 0, and allow
 that $g$ can have a point mass at 0, corresponding to the ``null" effects.
(An addition to our software implementation, due to C.Dai, allows the mode to be estimated from the data by maximum likelihood.)
Equation (\ref{eqn:beta}) assumes that the $\beta_j$ all come from the same distribution $g$, independent of $\shat_j$.
This can be relaxed to allow the distribution of $\beta_j$ to depend on $\shat_j$ using
 \begin{equation} \label{eqn:beta-alpha}
 \frac{\beta_j}{\shat_j^\alpha} \, \big| \, g, \shat \sim g(\cdot) \quad \text{independently for $j=1,\dots,J$}
 \end{equation}
for any $\alpha \geq 0$. Setting $\alpha=0$ yields (\ref{eqn:beta}), and setting $\alpha=1$ corresponds to
assuming that the ``standardized effects" $\beta_j/ \shat_j$ have a common distribution. This case is of special interest:
it effectively corresponds to the ``$p$ value prior" in \cite{wakefield:2009} and is, implicitly, 
the assumption made by existing methods that rank tests by their $p$ values (or $z$ scores). See Results for further discussion.

 Second, we assume that the observations $\bhat$ are independent given $\beta$,
 with $\bhat_j$ depending on $\beta,\shat$ only through $\beta_j$ and $\shat_j$:
 \begin{equation} \label{eqn:lik}
 \bhat_j \, | \, \beta, \shat \sim p(\bhat_j | \beta_j, \shat_j), \quad \text{independently for $j=1,\dots,J$.}
 \end{equation}
A natural assumption, made by \cite{wakefield:2009},  is that 
 \begin{equation} \label{eqn:normlik}
 \bhat_j \, | \, \beta_j, \shat_j \sim N(\beta_j, \shat_j),
 \end{equation}
 which should be a good approximation if the estimates $\bhat_j,\shat_j$ are based on a large number of observations.
 To try to improve this approximation when there are fewer observations we generalize this to
  \begin{equation} \label{eqn:lik}
 \bhat_j \, | \, \beta_j, \shat_j \sim T_\nu(\beta_j, \shat_j)
 \end{equation}
where $T_\nu(\beta_j,\shat_j)$ denotes the distribution of $\beta_j+\shat_j T_\nu$ where $T_\nu$ has a standard $t$ distribution on $\nu$ degrees of freedom,
and  $\nu$ denotes the degrees of freedom used to estimate $\shat_j$ (assumed known, and for simplicity assumed to be the same for each $j$).

Equation (\ref{eqn:lik}) is, of course, motivated by the standard asymptotic result
\begin{equation} \label{eqn:tdist}
(\bhat_j-\beta_j)/\shat_j \sim T_\nu.
\end{equation}
However (\ref{eqn:tdist}) does not imply (\ref{eqn:lik}), because in (\ref{eqn:tdist}) $\shat_j$ is random whereas in (\ref{eqn:lik}) it is conditioned on.
In principle it would be preferable, for a number of reasons, to model the randomness in $\shat_j$; we are
currently pursuing this improved approach in work with Mengyin Lu, and results will be published elsewhere. We note here that
modelling the randomness in $\shat_j$ is particularly helpful when the number of observations used to estimate $\shat_j$ is small (e.g. $<10$),
where our simpler approach can produce unsatisfactory results (see later).

Given the distribution $g$, the independence assumptions in (\ref{eqn:beta}) and (\ref{eqn:lik}) imply that the posterior distribution $\beta | g,\bhat,\shat$ conveniently 
factorizes into independent components $p(\beta | g,\bhat,\shat) = \prod_j p(\beta_j | g, \bhat_j, \shat_j)$.
The Empirical Bayes approach involves first estimating $g$ using all the data, and then computing quantities of interest conditional on the estimated $g$. That is:
 \begin{itemize}
 \item Estimate $g$ by maximising the likelihood $\hat{g} = \arg \max L(g)$ where $L(g) := p(\bhat | g, \shat)$ and the
 maximisation is subject to the constraint that $g$ is unimodal.
 \item Compute the conditional distributions $p(\beta_j | \hat{g} \bhat, \shat)$ ,
 from which we can compute all quantities of interest such as lfdr, lfsr, $q$-values, posterior credible intervals/regions etc.
  \end{itemize}

 \begin{note}
The conditional distributions $p(\beta_j | \hat{g}, \bhat, s)$ 
encapsulate uncertainty in the values for $\beta_j$, combining information across
$j=1,\dots,J$. The combining of the information occurs through estimation of
$g$, which involves all of the data.
In principle we might prefer a full Bayes approach that accounts for uncertainty in $g$; however,
we believe that in most practical applications uncertainty in $g$ will not be the most important concern, and 
compromise this principle for the simplicity of the EB approach.
\end{note}

\def\dt{\text{dt}}
\begin{note}
 A key property of the likelihood (\ref{eqn:lik}) [and indeed (\ref{eqn:normlik})] is that
observations with a large $\shat_j$ have an essentially flat likelihood, and so do not affect inference for
$g$ or the other effects. This contrasts with existing approaches that model the $p$ values or $z$ scores directly: observations with large $\shat_j$ will tend to produce 
$p$ values with approximately $U[0,1]$ distribution, and $z$ scores with an approximately $N(0,1)$ distribution, even under the alternative hypothesis (assuming
that the effect $\beta_j$ is small compared with $\shat_j$). These observations therefore do affect inference; specifically they add noise
and inflate estimates of the FDR. Because of this our approach can take better account of the informativeness of each measurement, as illustrated in Results below.
\end{note}

@@

 \begin{note}
Although the unimodal assumption (UA) will not apply to all situations, we argue that it will be reasonable in many practical contexts. 
For example, in contexts where interest focusses on which $\beta_j$ differ from zero, which suggests that ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible, and that the distribution of the effects will be unimodal about 0. 
Alternatively, we can motivate  the UA by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. 
Note that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

%Interestingly, although the unimodal assumption seems natural, much previous related work on estimating False Discovery Rates  
%has assumed, either explicitly or implicitly, that the distribution of effects is multimodal - see Figure \ref{fig:ZA}. 
Note that, although the UA appears novel in this context,
almost all analogous work in large-scale regression make the UA for the regression coefficents - 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{}.
One of our aims here is to emphasize the considerable practical benefits of making the UA in the FDR context.
\end{note}
%The $t$ likelihood (\ref{eqn:lik}) can derived from an assumption of conditional independence of the data on each effect given the true effects, plus two additional assumptions: a) $\bhat_j, \shat_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$); and b) $\shat_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\bhat_j, \shat_j | \beta) = p(\bhat | \beta, \shat_j) p(\shat_j | \beta)$, while the latter (b) suggests assuming that $p(\shat_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\bhat_j | \beta, \shat_j)$. If $\bhat_j, \shat_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\bhat_j,\shat_j$, rather than conditional on $D_j$. See \cite{johnson:2008} and \cite{wakefield:2009} for more general discussion and examples of Bayesian inference based on summary statistics.

@@

\subsubsection*{Implementation outline}

>>>>

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle, Bayesian approaches can naturally unify testing and estimation into a single framework -- testing is
simply estimation with some positive prior probability that the effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice, large-scale studies that assess many effects almost invariably focus on testing significance, and
controlling the FDR, rather than on estimating the sizes of the effect. 
The two new ideas highlighted above facilitate estimation as well as testing, and by providing easy-to-use software implementing our methods
we hope to promote and accelerate the shift in this direction.

@@

The $q$ value for observation $j$ is defined \cite{storey.03} as, roughly, the FDR for the set of observations that are at least as significant as observation $j$.
In a Bayesian analysis it is natural to order the significance of the hypotheses by $\fdr_j$, so we define
\begin{equation}
q_j := \widehat\FDR(\{k:\fdr_k \leq \fdr_j\}).
\end{equation}
%In simple settings (e.g. symmetric effects, with the same standard error) $\fdr_j$ is a monotonic function of the $p$ value $p_j$, and so
%\begin{equation}
%q_j = \widehat\FDR(\{k:p_k \leq p_j\})
%\end{equation}
%which is close to the definition in \cite{storey.03}.

\cite{gelman2012we} emphasise that there are settings where
$\beta_j=0$ is implausible, in which case the FDR is not useful: if every $\beta_j$ is non-zero then there
is no such thing as a false discovery and the FDR will always be identically 0. 
Gelman et.~al.~suggest that in such settings we should replace the concept of a false discovery with the
concept of an ``error in sign". The idea is that, in settings where $\beta_j=0$ is implausible, the most fundamental
inference objective is to ask which $\beta_j$ are positive and which are negative.
Indeed, even in settings where some
$\beta_j$ are exactly zero, separately identifying which are positive and which negative may be useful. For example, when identifying differentially expressed genes,
analysts will often separate the genes that are ``upregulated" from those that ``downregulated" in a condition.
Further, this idea has a long history: for example, \cite{tukey:xx}, p32, suggests one should address
\begin{quote}
...the more meaningful question: ``is the evidence strong enough to support a belief that the observed difference has the correct sign?"
\end{quote}

Motivated by this, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \bhat, s), p(\beta_j \leq 0| \hat\pi, \bhat, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Naturally, we consider it an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \bhat, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05.

Note that $\lfsr_j \geq \lfdr_j$ 
because both the events $\beta_j \geq 0$
and $\beta_j \leq 0$ include the event $\beta_j=0$.
Thus, lfsr gives an upper bound for lfdr.

Because our methods involve explicitly modelling effects $\beta_j$, rather than 
$p$ values or $z$ scores, they can provide estimates of the local false sign rates.
As show later, these estimates are much more robust to underlying assumptions than estimates
of the FDR or $\lfdr$. Thus, although for comparison with existing methods we have
focussed on FDR computations, in practice we strongly recommend using $\lfsr$ and not $\lfdr$.

@@

 Here we introduce an EB method, which, for reasons discussed above, we call ``adaptive shrinkage" or ``ash".
 The method provides not only estimated $\fdr_j$ and $q$ values, but also shrinkage point estimates and credible intervals for $\beta_j$,
 and estimates of the local false sign rates.

We begin by presenting the simplest version of our model, before embellishing it.
Instead of partitioning the (observed) $z$ scores or $p$ values into null and alternative components,
we use a model that partitions the (unobserved) effects $\beta_j$  into null and alternative components.
That is, letting $g$ denote the distribution of the effects $\beta_j$, we write
\begin{equation} \label{eqn:betaj}
g(\beta_j) = \pi_0 \delta_0 + (1-\pi_0) g_1(\beta_j)
\end{equation}
where $\delta_0$ denotes a point mass at 0, and $g_1$ denotes the (unknown) distribution of the non-zero $\beta_j$.
Thus $\pi_0$ denotes the proportion of effects that are null.

@@

Since the $\beta_j$ are unobserved, we need a model to connect the $\beta_j$ to observations. Here we
treat the estimates $\bhat_j$ as the observed data, and assume that they are noisy measurements of the true $\beta_j$ with given standard error
$\shat_j$:
\begin{equation} \label{eqn:normlik}
\bhat_j | \beta_j, \shat_j \sim N(\beta_j, \shat^2_j).
\end{equation}
This approach, which follows \cite{wakefield:2009}, 
should be a good approximation if $\bhat_j$ and $\shat_j$ are based on sufficiently many observations. We discuss below an improvement 
for moderate numbers of observations, based on replacing this normal likelihood with a $t$ likelihood.

Combining (\ref{eqn:betaj})-(\ref{eqn:normlik}), and assuming independence of the observations and effects for different $j$ (given $\shat, \pi_0,w_1,\dots,w_k$), yields
a hierarchical model for $\beta,\bhat$ given $\shat$, with unknown hyper-parameters $(\pi_0,w_1,\dots,w_k)$. To simplify notation we define $\pi_k := (1-\pi_0)w_k$ 
so that the unknown hyper-parameters can be written as a vector $\pi:=(\pi_0,\pi_1,\dots,\pi_K)$ whose elements are non-negative and sum to 1.
The usual empirical Bayes approach to fitting this model would involve two steps:
\begin{enumerate}
\item Estimate the hyperparameters $\pi$ by maximum likelihood, yielding a maximum likelihood estimate $\hat{\pi}$.
\item Compute quantities of interest (e.g. local fdr values, $q$ values, credible intervals etc.) from the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$.
\end{enumerate}
We make one modification to this procedure: instead of obtaining $\hat\pi$ by maximizing the likelihood, we instead maximise a penalized
likelihood, where the penalty (detailed below) encourages $\hat\pi_0$ to be as big as possible (within the constrains of the model and observed data). We use
this penalty here because in FDR appllications it is considered desirable to avoid underestimating $\pi_0$ so as to avoid underestimating the FDR. 
Both steps 1 and 2 are very straightforward: $\hat{\pi}$ can be obtained using a simple EM algorithm \cite{EM} to maximize the penalized likelihood, and the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$ are analytically available, each a mixture of a point mass on zero and $K$ normal distributions.
(Note that the simplicity of the EM algorithm in step 1 is due to our using a fixed grid for $\sigma_k$ in (\ref{eqn:g1}), instead of estimating $\sigma_k$,
which may seem more natural but is not straightforward when $\shat_j$ varies among $j$. This simple device may be useful in other applications.)

The conditional distributions $p(\beta_j | \hat{\pi}, \bhat_j, \shat_j)$ 
encapsulate uncertainty in $\beta_j$, combining information across {\it all} observations 
$j=1,\dots,J$. Specifically, the combining of the information occurs through estimation of
$\pi$, which involves all of the data. Importantly, when estimating $\pi$ our approach accounts for
the precision of each measurement through the likelihood (\ref{eqn:normlik}). For example, 
observations with a large $\shat_j$ have an essentially flat likelihood, and so have little effect on estimation of $\pi$, and
corresondingly little effect on the estimated FDR of other observations. 
We highlight this because it contrasts with approaches that model the $p$ values or $z$ scores directly: observations with large $\shat_j$ will tend to produce 
$p$ values with approximately $U[0,1]$ distribution, and $z$ scores with an approximately $N(0,1)$ distribution, under both the null and the alternative hypothesis (assuming
that the effect $\beta_j$ is small compared with $\shat_j$). Such noisy observations therefore do affect inference; specifically they add to the
estimated weight of the null component $\pi_0$, and inflate estimates of the FDR. 
Because of this our approach can take better account of the informativeness of each measurement, as illustrated in Results below.

\subsubsection*{Discussion on UA}

 Since we view the UA as a key assumption we briefly discuss it here.
Although the UA will not apply to all situations, we argue that it will be reasonable in many practical contexts, especially those
involving FDR where interest focusses on which $\beta_j$ differ from zero. This is because whenever ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to imagine that ``$\beta_j$ very near 0" is also plausible. From there it seems reasonable to imagine that larger effects become
decreasingly plausible, and so the distribution of the effects will be unimodal about 0. 
Alternatively, we can motivate  the UA by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. 
Note that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

%Interestingly, although the unimodal assumption seems natural, much previous related work on estimating False Discovery Rates  
%has assumed, either explicitly or implicitly, that the distribution of effects is multimodal - see Figure \ref{fig:ZA}. 
In addition, we note that although the UA is not made by any commonly-used existing FDR methods,
almost all analogous work in sparse regression models make the UA for the regression coefficents - 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{}.
(These are all less flexible than the approach we take here, which provides for general uni-modal distributions, and 
it may be fruitful to apply our methods to the regression context; indeed see \cite{goddard} for work in this vein.) 
The UA assumption on regression coeffients is directly analagous to our UA for effects, and so we view its
widespread use in the regression context as supporting its use here.

In addition to these arguments, the UA also has a considerable practical benefit: it produces very simple procedures that are both computationally
and statistically stable. We illustrate these features in Results.

@@

\subsubsection*{More flexible unimodal distributions}

To provide a more general approach to defining the distribution of effects $g(\beta_j)$, consider 
\begin{equation} \label{eqn:g}
g(\cdot; \pi) = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k f_k(\cdot) 
\end{equation}
where $f_k$ are pre-specified component distributions with one of the following forms: 
\begin{enumerate}[(i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$,
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$,
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
(In (iii) we include both components in the mixture (\ref{eqn:g}), so for a grid of values $a_1,\dots,a_K$ there
are actually $2K+1$ components in the mixture.)
The version of our model described above corresponds to (i).
Replacing these with uniform components (ii)-(iii) only slightly complicates calculations
under the normal likelihood (\ref{eqn:normlik}), and greatly simplifies the calculations under the $t$ likelihood
(\ref{eqn:tlik}) introduced below.
Our use of uniform components here closely mirrors \cite{cordy1997deconvolution}.

Moving from (i) to (iii) the representation (\ref{eqn:g}) becomes increasingly flexible. Indeed,
using a large dense grid of $\sigma^2_k$ or $a_k$, we can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[(i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in  high-dimensional regression settings.
\item any symmetric unimodal distribution about 0.
\item any unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to \cite{khintchine:1938} and  \cite{shepp:1962}; see \cite{feller:1971}, page  158. 
In other words, (ii) and (iii) provide fully non-parametric estimation for $g$ under the constraints that it is (ii) both unimodal and symmetric, or (iii) unimodal only.

Although our discussion above emphasises the use of large $K$, in practice modest values of $K$ can provide reasonable performance. 
The key point is that the value of $K$ is not critical provided it is sufficiently large, and the grid of $\sigma_k$ or $a_k$ values suitably chosen.
See Section \ref{details} for our software defaults.

%Although it is natural to worry about ``overfitting" if $K$ is large,  in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal constraint is sufficiently strong that there will exist a non-parametric maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $\shat_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander1956theory}.)
%Thus allowing $K$ to be large in ii) or iii), and maximizing the likelihood with respect to $\pi$, will approximate the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

We can generalize the normal likelihood assumption (\ref{eqn:normlik}) by replacing it with a $t$ likelihood:
  \begin{equation} \label{eqn:tlik}
 \bhat_j \, | \, \beta_j, \shat_j \sim T_\nu(\beta_j, \shat_j)
 \end{equation}
where $T_\nu(\beta_j,\shat_j)$ denotes the distribution of $\beta_j+\shat_j T_\nu$ where $T_\nu$ has a standard $t$ distribution on $\nu$ degrees of freedom,
and  $\nu$ denotes the degrees of freedom used to estimate $\shat_j$ (assumed known, and for simplicity assumed to be the same for each $j$).
The normal approximation (\ref{eqn:normlik}) corresponds to the limit $\nu \rightarrow \infty$.
This generalization does not complicate inference when used with mixtures of uniform components for $g$ in (\ref{eqn:g}).
For normal components the computations with a $t$ likelihood are considerably more difficult and we have not implemented this combination.

Equation (\ref{eqn:tlik}) is, of course, motivated by the standard asymptotic result
\begin{equation} \label{eqn:tdist}
(\bhat_j-\beta_j)/\shat_j \sim T_\nu.
\end{equation}
However (\ref{eqn:tdist}) does not imply (\ref{eqn:tlik}), because in (\ref{eqn:tdist}) $\shat_j$ is random whereas in (\ref{eqn:tlik}) it is conditioned on.
In principle it would be preferable, for a number of reasons, to model the randomness in $\shat_j$; we are
currently pursuing this improved approach in work with Mengyin Lu, and results will be published elsewhere. We note here that
modelling the randomness in $\shat_j$ is particularly helpful when the number of observations used to estimate $\shat_j$ is very small (e.g. $<10$),
where our simpler approach can produce unsatisfactory results (see later).

\subsubsection*{Dependence of effects on standard errors}

Equation (\ref{eqn:betaj}) assumes that the $\beta_j$ all come from the same distribution $g$, independent of $\shat_j$.
This can be relaxed to allow the distribution of $\beta_j$ to depend on $\shat_j$ using
 \begin{equation} \label{eqn:beta-alpha}
 \frac{\beta_j}{\shat_j^\alpha} \, \big |  \shat_j \sim g(\cdot)
 \end{equation}
for any $\alpha \geq 0$. Setting $\alpha=0$ yields (\ref{eqn:beta}), and setting $\alpha=1$ corresponds to
assuming that the $t_j =\beta_j/ \shat_j$ have a common distribution. This case is of special interest:
it effectively corresponds to the ``$p$ value prior" in \cite{wakefield:2009} and is, implicitly, 
the assumption made by existing FDR methods that rank tests by their $p$ values (or $z$ or $t$ scores). See Results for further discussion.

The model \ref{eqn:beta-alpha} for general $\alpha$ is actually easily fitted using the algorithm for $\alpha=0$. 
To see this, define $b_j:= \beta_j/ \shat_j^\alpha$, and $\hat{b} := \bhat_j/\shat_j^\alpha$. Then $\hat{b}_j$ is an estimate of $b_j$ with
 standard error $\shat'_j:=\shat_j^{1-\alpha}$. 
 Applying the algorithm for $\alpha=0$ to effect estimates $\hat{b}_1,\dots,\hat{b}_J$ with standard errors $\shat'_1,\dots,\shat'_J$
yields a posterior distribution $p(b_j | \shat_j, \hat{b}_j, \hat{\pi}, \alpha)$, which induces a posterior distribution on $\beta_j = b_j \shat_j^\alpha$.
In the special case $\alpha=1$, $\hat{b}_j$ is the $t$ score $t_j$ and $\shat'{b}=1$, so this involves applying our algorithm to the $t$ scores
treating them all as having the same standard error. In this case the local fdr from our method becomes monotonic in each direction as
the $t$ score increases away from zero, just as with \qvalue, and (usually) \mixfdr and \locfdr.

Different values of $\alpha$ in (\ref{eqn:beta-alpha}) essentially correspond to different models for
how effect sizes $\beta_j$ scale with the standard error $\shat_j$. Since this scaling is unknown it may be desirable to estimate
it from the data, and this can be done here by jointly maximizing the likelihood $p(\hat{b} | \shat,\pi,\alpha)$ over $\pi$ and $\alpha$
rather than just $\pi$.  Although values of $\alpha$ other than 0 and 1 may not be easy interpret,
and the actual relationship between $\beta_j$ and $\shat_j$ is unlikely to exactly follow (\ref{eqn:beta-alpha}) for any $\alpha$,
this approach seems preferable in practice than simply assuming $\alpha=0$ or $\alpha=1$. For brevity we
do not investigate this idea any further here, but it has been implemented in our software by C.Dai, using a simple grid search over $\alpha$.

\subsubsection*{Non-zero mode}

An addition to our software implementation, due to C.Dai, allows the mode to be estimated from the data by maximum likelihood.

\subsection*{Implementation Details}

See Section \ref{sec:implement} for further implementation details.

\def\dt{\text{dt}}

@@

%The $t$ likelihood (\ref{eqn:lik}) can derived from an assumption of conditional independence of the data on each effect given the true effects, plus two additional assumptions: a) $\bhat_j, \shat_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$); and b) $\shat_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\bhat_j, \shat_j | \beta) = p(\bhat | \beta, \shat_j) p(\shat_j | \beta)$, while the latter (b) suggests assuming that $p(\shat_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\bhat_j | \beta, \shat_j)$. If $\bhat_j, \shat_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\bhat_j,\shat_j$, rather than conditional on $D_j$. See \cite{johnson:2008} and \cite{wakefield:2009} for more general discussion and examples of Bayesian inference based on summary statistics.

@@
